The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
add ref for some metrics
add ref for ml eig centrality

We generated all networks 
Right now, we calculate mostly degree/neighborhood based metrics. 
* Degree centrality
* Multidegree
* Degree deviation: standard deviation of degree across layers

@@

Finally, some weighted variable.

>>>>

We generated all networks 
Right now, we calculate mostly degree/neighborhood based metrics.

Reference for extending degree centrality to multilayer, neighbors, connective redundancy and relevance: Berlingerio 2011 "Foundations of multidimensional..."

* Degree centrality
* Multidegree
* Degree deviation: standard deviation of degree across layers

@@

Finally, some weighted variables:

* eigenvector centrality, summed across layers as described in Boccaletti, Stefano, et al. "The structure and dynamics of multilayer networks." Physics Reports 544.1 (2014): 1-122.
